Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-06-12 intro.tex
Revision de los trabajos relacionados, y reagrupamiento con ideas de la introduccion.  Redundancias eliminadas y alguna informacion de mas eliminada

The past and present rates of disease development can in principle be
used to predict its future behavior and to determine if a particular
fungicide spray program will be able to effectively treat the disease
in an economically affordable way \citep{ChuangJeger1987}.
%
Phytopathological studies point out that climate has a major effect on
the development of the black Sigatoka, where the main variables
affecting it are precipitation, temperature, relative humidity and
wind \citep{MarinVargas1995}.  Hence, it can be expected that patterns
in these variables correlate with the disease development.

There exist already several efforts to apply machine learning methods
to support decision-making in agriculture, including the control of
crop diseases. For example, \cite{Camargo2012} present an intelligent
system for the assessment of crop disorders, \cite{Huang2010}
introduce a plant virus identification method based on neural networks
with an evolutionary preprocessing stage, \cite{Kim2014} summarize in
their survey crop pests prediction methods using regression and
machine learning approaches, while \cite{Zhao2013} present an
intelligent agricultural forecasting system based on wireless sensor
networks.

\TODO{Importantísimo es explicar aquí brevemente por qué esos otros
  trabajos no se aplican al caso de la Sigatoka, o qué es lo que han
  hecho mal, que este trabajo sí hace bien.}

>>>>

The past and present rates of disease development can in principle be
used to predict its future behavior and to determine if a particular
fungicide spray program will be able to effectively treat the disease
in an economically affordable way \citep{ChuangJeger1987}.
%
Phytopathological studies point out that climate has a major effect on
the development of the black Sigatoka, where the main variables
affecting it are precipitation, temperature, relative humidity and
wind \citep{MarinVargas1995}.  It can be expected that patterns in
these variables correlate with the disease development and hence its
automated discovery can support decision-making in the control of crop
diseases.

### 2016-06-12 methodology.tex
Revision de los trabajos relacionados, y reagrupamiento con ideas de la introduccion.  Redundancias eliminadas y alguna informacion de mas eliminada

\subsection{Data}
We use data acquired in two research farms of Corbana in Costa Rica: 1) 28 Millas (previously called Waldeck and located at Matina) and La Rita (located at Pococí), both in the province of Limón, Costa Rica. The banana type is Musa AAA, subgroup Cavendish, cv. Grande Naine. The \tablename $.$\ref{tabla1} shows the variables available.

>>>>

\subsection{Data}
We use data acquired in two research farms of Corbana in Costa Rica:
\emph{28 Millas} located in Matina and previously called
\emph{Waldeck}, and \emph{La Rita} located in Pococí, both in the
province of Limón, Costa Rica. The banana type is Musa AAA, subgroup
Cavendish, cv. Grande Naine. The \reftab{tabla1} shows the
variables available.

### 2016-06-12 related.tex
Cambios menores
Revision de los trabajos relacionados, y reagrupamiento con ideas de la introduccion.  Redundancias eliminadas y alguna informacion de mas eliminada

Huang et al. \citep{Huang2010}  surveyed the development of soft computing techniques in agricultural and biological engineering, including fuzzy logic, artificial neural networks, genetic algorithms, bayesian inference and decision trees.

A related work, proposed by Romero \citep{Romero1995} relies on regression models using a stepwise procedure to predict incubation and latency times of black Sigatoka. The author performed experiments on two farms located in Costa Rica (La Rita and Waldeck, the same as those used in this study but with different names). The study used data from: December 1993 to August 1995. Romero concluded that the model to predict the incubation period accounted a $R^2$ of 69\% in his observed data but it was not a good predictor when it was validated against an independent dataset (cross validation). For latency, he developed two models that accounted a $R^2$ of 78\% in the observed data, however, when validated against an independent dataset (cross validation), for La Rita obtained an adjusted $R^2$ of 82\%, and for Weldeck, none of the models satisfactorily predicted the latent period; and then those predictions were not shown \citep{Romero1995}.

Glezakos et al. \citep{Glezakos2010} proposed to use Genetic Algorithms (GA) and Neural Networks (NN) to identify plant virus (Tobacco Rattle Virus (TRV) and the Cucumber Green Mottle Mosaic Virus (CGMMV)). This is achieved by the development of ana- lytical tools of evolutionary adaptive width, propelled by Genetic Algorithms (GAs) and Neural Networks (NNs). The method was tested against some of the most commonly used classifiers in machine learning (Bayes, Trees and k-NN) via cross-validation and proved its potential towards the identification.

In the agricultural context, Alves et al. \citep{Alves2011} used  geoinformation techniques to develop predictive models to study the areas of risk to soybean rust in soybean, coffee leaf rust in coffee, and black Sigatoka in banana, considering Brazil’s climatic characterization and the distribution of soybean, coffee and banana crops. Temperature and rainfall data were obtained for the period from 1950 to 2000, and of simulations for 2020, 2050 and 2080 using the SRES A2 climate change scenarios. Using principal components analysis, a single variable was generated based on 57 variables, in order to determine an index explaining 87\%, 88\% and 90\% of the variability of soybean, coffee and banana crops, respectively, in municipal districts across Brazil. The climatic model was used to generate the zoning of the three plant diseases, using temperature and leaf wetness as input. Areas of favorability for the diseases were plotted against the main coffee, soybean and banana growing areas in Brazil. This methodology enabled the visualization of the changes in areas favorable for epidemics under possible future scenarios of climate change.

@@

Furthermore, there have been attempts to generate software tools. Camargo et al. \citep{Camargo2012} presented an information system for the assessment of plant disorders (Isacrodi). They proposed that experts will attain a much better accuracy than the Isacrodi classifier, particularly when provided with samples from the affected crop. However, those cases where such expertise is not available, they suggest that Isacrodi can provide valuable support to farmers. Isacordi includes 15 crop disorders, but the black Sigatoka no is one of them. The prediction process is based on multi-class support vector machines.

Regarding the prediction of the develpment of the black Sigatoka with machine learning methods, Bendini et al. \citep{Bendini2013}  presented a study about the risk analysis of black Sigatoka occurrence based on polynomial models. A case study was developed in a commercial banana plantation located in Jacupiranga, Brazil. It was monitored weekly during the period from February to December 2005. Data included the weekly monitoring of the disease’s evolution stage, time series of meteorological data and remote sensing data. They obtained a model to estimate the evolution of the disease from satellite imagery. This model relates gray levels (NC) of the band 2 images of the Landsat-5 satellite, with the progress status or disease severity (EE). The authors claim to reach an $R^2$ of 90\%.

Also there are works related to banana fruit. Soares et al. \citep{Soares2014} apply two techniques: artificial neural networks (ANNs) and multiple linear regression (MLR) in banana plant to predict the yield, their results show that the neural network proved to be more accurate in forecasting the weight of the bunch in comparison to the multiple linear regressions in terms of the mean prediction-error $(MPE = 1.40)$, mean square deviation $(MSD = 2.29)$ and coefficient of determination $(R^2 = 91\%)$.

In general, the machine learning methods applied to predict the evolution of plant diseases, can be classified in two main approaches: 1) Those whose main inputs are images, and 2) Those whose main inputs are environmental and biological variables. Our study focuses in the second case.

>>>>

Several efforts have been made to apply machine learning techniques in
the automated discovery of relationships between environmental
variables and quantified descriptors for variables of agricultural 
interest such as the progress of diseases.
% 
\citet{Huang2010} summarize in their survey the
development of soft computing techniques in agricultural and
biological engineering, including fuzzy logic, artificial neural
networks, genetic algorithms, bayesian inference and decision trees.
%
Similarly, \citet{Kim2014} survey more recent prediction
methods for crop pests using regression and machine learning approaches.

\TODO{Falta indicar qué concluyen los dos surveys anteriores}

In general, the machine learning methods applied to predict the
evolution of plant diseases, can be classified in two main approaches:
1)~those whose main inputs are images, and 2)~Those whose main inputs
are environmental and biological variables. Our study focuses in the
second case.

% %
% For example, 
% 
% Me parece que aquí hay un error: Huang2010 es el survey, y sería mucha
% coincidencia que fuera lo mismo que el \citet{Glezakos2010} ¿o no?
%
% \cite{Huang2010} introduce a plant virus
% identification method based on neural networks with an evolutionary
% preprocessing stage, 
%

\citet{Romero1995} relied on regression models using a stepwise
procedure to predict incubation and disease latency periods for the
black Sigatoka.
% 
He collected environmental data from two different farms in Costa Rica
between December 1993 and August 1995.
%
The prediction models reached coefficients of determination $R^2$ of
69\% or 78\% on the observed data for the incubation and disease
latency periods, respectively; however, the cross validation on
independent data sets failed.

More recently, \citet{Glezakos2010} used genetic algorithms (GA) and
neural networks (NN) to identify the Tobacco Rattle Virus (TRV) and
the Cucumber Green Mottle Mosaic Virus (CGMMV).
%
The method was tested against some of the most commonly used
classifiers in machine learning (Bayes classifiers, decision trees and
$k$-nearest neighbors) via cross-validation and proved their
applicability in these kind of problems.

\citet{Alves2011} used geoinformation techniques to
develop predictive models in the study of risk areas to soybean rust,
coffee leaf rust, and banana black Sigatoka, under consideration of
Brazil’s climatic characteristics and the distribution of soybean,
coffee and banana crops.
%
Temperature and rainfall data were acquired for the period from 1950
to 2000, and simulated data were generated for 2020, 2050 and 2080
using the SRES~A2 climate change scenarios.
%
Using principal components analysis, a single variable was generated
as a linear combination of 57 input variables, in order to determine
an index explaining 87\%, 88\% and 90\% of the
%
\todofn{variability}{variabilidad de qué?}  
%
of soybean, coffee and
banana crops, respectively, in municipal districts across Brazil.
%
The climatic model was used to generate the zoning of the three plant
diseases, using temperature and leaf wetness as input.
%
%Redunda con lo que sigue:
%Areas favorable for the diseases were plotted against the main coffee,
%soybean and banana growing areas in Brazil.
%
This methodology enabled the visualization of the changes in areas
favorable for epidemics under possible future scenarios of climate
change.

@@

Furthermore, there have been attempts to generate software
tools. \citet{Camargo2012} presented an information
system for the assessment of plant disorders (Isacrodi).
%
They showed that human experts will attain a much accurate assessment
than the Isacrodi classifier, particularly when provided with samples
from the affected crop. However, in those cases where such expertise
is not available, the authors suggest that Isacrodi can still provide
valuable support to farmers.
%
Isacordi includes 15 crop disorders, but the black Sigatoka is none
of them. The prediction process is based on multi-class support vector
machines.

Regarding the prediction of the black Sigatoka disease development
with machine learning methods, \citet{Bendini2013} presented a study
on the risk analysis of its occurrence based on polynomial models.
%
A case study was developed in a commercial banana plantation located
in Jacupiranga, Brazil. It was monitored weekly from February to
December 2005.
%
The data included the weekly monitoring of the disease’s evolution
stage, time series of meteorological data and remote sensing
data.
%
They obtained a model to estimate the evolution of the disease from
satellite imagery. This model relates gray levels (NC) of the band 2
images of the Landsat-5 satellite, with the progress status or disease
severity (EE). The authors claim to reach an $R^2$ of 90\%.

There are also works related to the banana fruit. \citet{Soares2014}
apply two techniques: artificial neural networks (ANNs) and multiple
linear regression (MLR) in banana plant to predict the yield.
%
Their results show that the neural network is more accurate in
forecasting the weight of the bunch in comparison to the multiple
linear regressors in terms of the mean prediction-error $(MPE =
1.40)$, mean square deviation $(MSD = 2.29)$ and coefficient of
determination $(R^2 = 91\%)$.

% Este no calza, porque no se ve qué es lo de machine learning que usa...
%
%\citet{Zhao2013} present an intelligent agricultural
%forecasting system based on wireless sensor networks.

\TODO{Importantísimo es explicar aquí brevemente por qué esos otros
  trabajos no se aplican al caso de la Sigatoka, o qué es lo que han
  hecho mal, que este trabajo sí hace bien.}
